\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-15 papers/jss/article.Rnw
Add back the article 'the' in the second sentence of the introduction, and revert back to my use of 'different' rather than various.
I believe this flows better but don't have a strong preference if
someone can explain why they like the change.

Adding the article 'the' makes it more concrete/definitive.  Certainly
others could come up with a different break down of the phases of data
analysis, but that doesn't make our breakdown wrong, and thus I see no
reason to avoid the article 'the' here, if that was indeed the reason
for the change.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/

Modern data collection and analysis pipelines increasingly involve collections
of decoupled components in order to better manage software complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
% This is really a different pattern not connected well here.
%Data analysis patterns such as Split-Apply-Combine
%\citep{wickham2011split} explicitly break up large problems into manageable pieces.  
These pipelines are frequently built using different programming 
languages for various phases of data analysis -- collection, 
cleaning, modeling, analysis, post-processing, and
presentation in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
each environment or language. Every stage of such a data
analysis pipeline may produce intermediate results that need to be
stored or sent over the network for further processing. 
% JO Perhaps also mention that serialization is needed for distributed
% systems to make systems scale up?

>>>>

Modern data collection and analysis pipelines increasingly involve collections
of decoupled components in order to better manage software complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
% This is really a different pattern not connected well here.
%Data analysis patterns such as Split-Apply-Combine
%\citep{wickham2011split} explicitly break up large problems into manageable pieces.  
These pipelines are frequently built using different programming 
languages for the different phases of data analysis -- collection,
cleaning, modeling, analysis, post-processing, and
presentation in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
each environment or language. Every stage of such a data
analysis pipeline may produce intermediate results that need to be
stored or sent over the network for further processing. 
% JO Perhaps also mention that serialization is needed for distributed
% systems to make systems scale up?
